### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0e0d41cde16c07b04c9d5e5f4f0fa52d636046ad 🚀

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\bold x, \bold y\$ of the spatial boundaries delineating the system,
whereas time is the time interval \$ \bold t\$ during which interactions
were sampled or for which they were predicted. We put these variables in
bold to emphasize that they are not single values, but rather continued
dimensions that could be outlined differently depending on the study
system. Regardless of how they were defined, they always delineate a
specific area \(A\) and duration \(D\). These could refer to the sampled
area and duration or to the targeted location and time period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence, which describes if both species can be found at location
and time \$ \bold x, \bold y, \bold t\$. Surely, the probability that
the interaction is realized must be \(0\) when species do not co-occur.
Similarly, species relative abundance is another important predictor of
the probability of interaction, because it impacts the probability that
species will randomly encounter (Canard \emph{et al.} 2012; Canard
\emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
probabilities can also be conditional on other biological and
environmental variables, such as temperature, precipitation, presence of
shelters, phenotypic plasticity, phenology, and presence of other
interacting species in the network. These conditions can affect species
traits, which greatly impact the likelihood of interactions (Poisot
\emph{et al.} 2015). When probabilities of interactions are estimated
using specific values of these variables, ecologists should make them
explicit in their metadata, preferably using mathematical equations to
avoid any ambiguity. In the next section, we will see examples of why
this matters when it comes to spatial, temporal, and taxonomic scaling
of biotic interactions. Here, we will use the variable \(\bold \Omega\)
as a substitute for the biological and ecological context in which
interaction probabilities were estimated. This gives us the following
equation for the probability that species (or taxa) \(i\) and \(j\)
interact in a local network \(N\):

\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega).}\label{eq:local}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega) \le P_M(i
\rightarrow j).}\label{eq:switch}\end{equation}

>>>>

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\mathbf x, \mathbf y\$ of the spatial boundaries delineating the system,
whereas time is the time interval \$ \mathbf t\$ during which
interactions were sampled or for which they were predicted. We put these
variables in bold to emphasize that they are not single values, but
rather continued dimensions that could be outlined differently depending
on the study system. Regardless of how they were defined, they always
delineate a specific area \(A\) and duration \(D\). These could refer to
the sampled area and duration or to the targeted location and time
period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence, which describes if both species can be found at location
and time \$ \mathbf x, \mathbf y, \mathbf t\$. Surely, the probability
that the interaction is realized must be \(0\) when species do not
co-occur. Similarly, species relative abundance is another important
predictor of the probability of interaction, because it impacts the
probability that species will randomly encounter (Canard \emph{et al.}
2012; Canard \emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
probabilities can also be conditional on other biological and
environmental variables, such as temperature, precipitation, presence of
shelters, phenotypic plasticity, phenology, and presence of other
interacting species in the network. These conditions can affect species
traits, which greatly impact the likelihood of interactions (Poisot
\emph{et al.} 2015). When probabilities of interactions are estimated
using specific values of these variables, ecologists should make them
explicit in their metadata, preferably using mathematical equations to
avoid any ambiguity. In the next section, we will see examples of why
this matters when it comes to spatial, temporal, and taxonomic scaling
of biotic interactions. Here, we will use the variable \(\bold \Omega\)
as a substitute for the biological and ecological context in which
interaction probabilities were estimated. This gives us the following
equation for the probability that species (or taxa) \(i\) and \(j\)
interact in a local network \(N\):

\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega).}\label{eq:local}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega) \le P_M(i
\rightarrow j).}\label{eq:switch}\end{equation}
